---
title: "Summary Gen4R"
execute:
  echo: false
author: Anthony Pompetti
date: "26-Feb-2024"
date-format: long
format: 
  revealjs:
    theme: simple
    embed-resources: true
---

```{r setup, include = FALSE}
library(tidyverse)
library(VariantAnnotation)
library(vcfR)
setwd("/home/anthony/data/12Feb2024_Concordance_Analysis")
library(here)
library(ggplot2)
library(ggridges)
library(gt)
```

```{r load_vcf, include = FALSE}
vcf <- readRDS(here("results/01/vcfR.rds"))
vcf <- vcf[samples = c("HM24385", "HM26105", "HM27730")]
```

## Compare HG002: HM24385, HM26105, HM27730 {style="font-size: 16px;"}
- HM24385: LCL
- HM26105: iPSC from LCL
- HM27730: iPSC from PBMC

## Compare HG002: HM24385, HM26105, HM27730 {style="font-size: 16px;"}
### Compare genotype quality {style="font-size: 16px;"}
```{r load_gq, include = FALSE}
gq <- extract.gt(vcf, element = "GQ")
```

```{r plot_gq}
data <- gq %>% 
    as_tibble(rownames = "chr_range") %>%
    pivot_longer(cols = -chr_range, names_to = "sample", values_to = "value") %>%
    mutate(value = as.numeric(value)) %>%
    mutate(value_bin = cut(value, breaks = c(0,10,20,30,40,50,60,70), include.lowest = TRUE))

p <- ggplot(
  data,
  aes(
    x = value,
    y = sample
  )
) +
stat_binline(scale = 1, binwidth = 1)

p
```

## Compare HG002: HM24385, HM26105, HM27730 {style="font-size: 16px;"}
### Compare genotype quality table format {style="font-size: 16px;"}
```{r gq_tbl}
tbl <- data %>%
  group_by(sample, value_bin) %>%
  dplyr::count() %>%
  ungroup() %>%
  pivot_wider(names_from = "sample", values_from = "n")

tbl %>%
  gt::gt(rowname_col = "value_bin") %>%
  gt::opt_interactive()
```

## Compare HG002: HM24385, HM26105, HM27730 {style="font-size: 16px;"}
### Compare depth {style="font-size: 16px;"}
```{r load_dp, include = FALSE}
dp <- extract.gt(vcf, element = "DP")
```

```{r plot_dp}
data <- dp %>% 
    as_tibble(rownames = "chr_range") %>%
    pivot_longer(cols = -chr_range, names_to = "sample", values_to = "value") %>%
    mutate(value = as.numeric(value)) %>%
    mutate(value_bin = cut(value, breaks = c(0,100,200,300,400,500,600),include.lowest = TRUE))

p <- ggplot(
  data,
  aes(
    x = value,
    y = sample
  )
) +
stat_binline(scale = 1, binwidth = 1)

p
```

## Compare HG002: HM24385, HM26105, HM27730 {style="font-size: 16px;"}
### Compare depth table format {style="font-size: 16px;"}
```{r dp_tbl}
tbl <- data %>%
  group_by(sample, value_bin) %>%
  dplyr::count() %>%
  ungroup() %>%
  pivot_wider(names_from = "sample", values_from = "n")

tbl %>%
  gt::gt(rowname_col = "value_bin") %>%
  gt::opt_interactive()  
```